Concurrent Programming with CXL

### 2020-06-16 book/paper.tex
Added alternating bit protocol implementation
Added actor code

@@

>>>>

\chapter{Actors}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/actor.cxl}
\end{code}
\caption{[actor.cxl] A producer/consumer actor.}
\label{fig:actor}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/actortest.cxl}
\end{code}
\caption{[actortest.cxl] Test code for producer/consumer actor.}
\label{fig:actortest}
\end{figure}

@@

\chapter{Networking: Alternating Bit Protocol}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/abp.cxl}
\end{code}
\caption{[abp.cxl] Alternating Bit Protocol.}
\label{fig:abp}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/abptest.cxl}
\end{code}
\caption{[abptest.cxl] Test code for alternating bit protocol.}
\label{fig:abptest}
\end{figure}
